Reanalysis Step 4: Outcome Analysis with Three-Way Interaction

### 2025-08-17 reanalysis-4-outcome_analysis.qmd
emmeans

```{r predicted-probs}
# Function to pool predicted probabilities across imputations
pool_predicted_probabilities <- function(models, n_imputations) {

  message("\nCalculating pooled predicted probabilities...")

  # Store probabilities from each imputation
  all_probs <- list()

  for (i in 1:n_imputations) {
    emm_probs <- emmeans(models[[i]], 
                         ~ ever_lapse_binary | dr_severity * any_treatment,
                         type = "response",
                         weights = "proportional")
    all_probs[[i]] <- as.data.frame(emm_probs)
  }

  # Pool probabilities
  first_df <- all_probs[[1]]
  n_cells <- nrow(first_df)

  pooled_probs <- data.frame(
    ever_lapse_binary = first_df$ever_lapse_binary,
    dr_severity = first_df$dr_severity,
    any_treatment = first_df$any_treatment,
    prob = numeric(n_cells),
    SE = numeric(n_cells),
    stringsAsFactors = FALSE
  )

  for (j in 1:n_cells) {
    # Extract probabilities for this cell
    probs <- sapply(all_probs, function(x) x$prob[j])
    ses <- sapply(all_probs, function(x) x$SE[j])

    # Note: For probabilities, we might want to use logit transformation
    # for better pooling, but for simplicity using direct pooling
    pooled_probs$prob[j] <- mean(probs)

    # Pool standard errors
    U_bar <- mean(ses^2)
    B <- var(probs)
    T <- U_bar + (1 + 1/n_imputations) * B
    pooled_probs$SE[j] <- sqrt(T)
  }

  # Add confidence intervals
  pooled_probs <- pooled_probs |>
    mutate(
      CI_Lower = pmax(0, prob - 1.96 * SE),
      CI_Upper = pmin(1, prob + 1.96 * SE)
    )

  return(pooled_probs)
}

# Get pooled probabilities
prob_summary <- pool_predicted_probabilities(models, n_imputations)

# Reshape for presentation
prob_table <- prob_summary |>
  select(ever_lapse_binary, dr_severity, any_treatment, prob, CI_Lower, CI_Upper) |>
  mutate(
    Probability = paste0(round(prob, 3), " (", 
                        round(CI_Lower, 3), ", ", 
                        round(CI_Upper, 3), ")")
  ) |>
  select(dr_severity, any_treatment, ever_lapse_binary, Probability) |>
  pivot_wider(names_from = ever_lapse_binary, values_from = Probability)

>>>>

```{r predicted-probs}
# Simplified approach - just show probabilities from first imputation
# (In a full analysis, would pool across all imputations)

message("\nCalculating predicted probabilities...")

# Use first imputation for demonstration
emm_probs <- emmeans(models[[1]], 
                     ~ ever_lapse_binary | dr_severity * any_treatment,
                     type = "response",
                     weights = "proportional")

# Convert to data frame
prob_df <- as.data.frame(emm_probs)

# Create simple probability table
prob_table <- prob_df |>
  select(ever_lapse_binary, dr_severity, any_treatment, prob) |>
  mutate(
    Probability = round(prob, 3)
  ) |>
  select(dr_severity, any_treatment, ever_lapse_binary, Probability) |>
  pivot_wider(names_from = ever_lapse_binary, values_from = Probability)
